Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure - Supplementaty materials

### 2012-11-24 paper.tex
First version of reply to referees sent to Ib

Already the early theretical descriptions of the possibility of oscillationary beheaviour even very simple catalytic systems (eg \cite{LAGOS1979,IVANOV1980,TAKOUDIS1981,SONG1991}) noticed that even though oscillation can theoretically occur in many catalytic systems, the details are extremely specific to the given system, and it can thus be diffuctult to predict how and if a given system will oscillate.

Oscillations in catalytic systems can be quite complex and the parameter space can be very large\cite{Ferino1999}. In the system investigated in this paper, oscillations could be dependant on morphologic parameres of the nanoparticels such as size, shape and exposed facets. Also the oxidation state and possible carbon pollution on the surface could have impact on the system. More macroscopic parameters such as the geometry of the reactor, the temperature distribution and the distribution of the particles throughout the reactor will influcence the systems' ability to show kinetic oscillations.

Oscillating reactions on single crystals at UHV conditions have been studied extensively and is know to originate from surface reconstructions of the surface during the oscillations\cite{Ertl2008}. It has previously been shown\cite{SALES1982} that CO oxidation at atmospheric pressures also shows oscillatory behavior on single crystals of Pt, Pd and Ir. Recent studies have proposed a mechanism on Pd \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface formation. CO oxidation oscillations has also been observed on Pt thin films\cite{Lund2000}, Pd zeolites\cite{Liauw1996,Slinko2001}, in macroscopic flow reactors\cite{Singh2010} and on Pt nanoparticles synthesized from wet chemical synthesis and subsequent annealing \cite{Carlsson2006}. Here we investigate CO oscillations in a microreactor model system on size selected Pt nanoparticles by high sensitivity mass spectrometry.

@@

In this study Pt nanoparticles were investigated which, compared to a single crystal or a thin film, is a very rough surface. It is to be expected that the particles will initially favor the reduced state. As the reaction runs the gas composition towards the outlet of the reactor will become more oxidizing increasing the oxidation rate of the particles (illustrated in Figure~\ref{fgr:full_oscillation}). Gradually, as the particles toward the outlet oxidizes the turn-over will increase and the general CO concentration will decrease promoting more and more particles to oxidize which will gradually be seen in the QMS as an increase in CO$_2$ and a decrease in CO. As the CO concentration decreases the light-off temperature will decrease hence approaching the constant temperature of the sample resulting in a steep increase in reactivity. It is important to note that the fraction of oxidized particles needed to achieve full conversion is not known. We are currently investigating new methods for gaining insight into the nature of the nanoparticles in the reactor but the low coverage and the design of the reactor !!! and the fact that the lid can only be removed by mechanically breaking the reactor!!! makes this a challenging task. If not all particles are oxidized at light-off they will now oxidize much faster due to the low CO-concentration. The further increased rate will not be visible in the QMS since the reactor is already in full conversion. As most of the particles are now oxidized they will become more and more roughened and gradually return to the reduced state. Fewer and fewer oxidized particles will be responsible for the activity increasing the roughing rate of the remaining active particles. Just before the overall activity drops only a fraction of the particles participates in the reaction and the deactivation will happen very suddenly. Once these potentially few particles eventually becomes sufficiently rough they will reduce and lose activity hence completing the oscillation cycle. It should be noted that our group has recently measured turnover frequencies of CO oxidation on Pt of almost $10^{5}$s$^{-1}$ per site corresponding to as little as $\sim$50000 Pt nanoparticles contributing to the reactivity just before the end of the high-activity cycle. This corresponds to an area of $\sim$0.5 ppm of the reactor area suggesting that in situ studies become challenging as such a minority of the reactor volume could account for all the reactivity. Attempts to see any thermal signal from such small areas has so far been in vain.

>>>>

!!!! Already the early theretical descriptions of the possibility of oscillationary beheaviour even very simple catalytic systems (eg \cite{LAGOS1979,IVANOV1980,TAKOUDIS1981,SONG1991}) noticed that even though oscillation can theoretically occur in many catalytic systems, the details are extremely specific to the given system, and it can thus be diffuctult to predict how and if a given system will oscillate. !!!!

!!! Oscillations in catalytic systems can be quite complex and the parameter space can be very large\cite{Ferino1999}. In the system investigated in this paper, oscillations could be dependant on morphologic parameres of the nanoparticels such as size, shape and exposed facets. Also the oxidation state and possible carbon pollution on the surface could have impact on the system. More macroscopic parameters such as the geometry of the reactor, the temperature distribution and the distribution of the particles throughout the reactor will influcence the systems ability to show kinetic oscillations. !!!

Oscillating reactions on single crystals at UHV conditions have been studied extensively and is know to originate from surface reconstructions of the surface during the oscillations\cite{Ertl2008}. It has previously been shown\cite{SALES1982} that CO oxidation at atmospheric pressures also shows oscillatory behavior on single crystals of Pt, Pd and Ir. Recent studies have proposed a mechanism on Pd \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface formation. CO oxidation oscillations has also been observed on Pt thin films\cite{Lund2000}, !!! Pd zeolites\cite{Liauw1996,Slinko2001} !!!, in macroscopic flow reactors\cite{Singh2010} and on Pt nanoparticles synthesized from wet chemical synthesis and subsequent annealing \cite{Carlsson2006}. Here we investigate CO oscillations in a microreactor model system on size selected Pt nanoparticles by high sensitivity mass spectrometry.

@@

In this study Pt nanoparticles were investigated which, compared to a single crystal or a thin film, is a very rough surface. It is to be expected that the particles will initially favor the reduced state. As the reaction runs the gas composition towards the outlet of the reactor will become more oxidizing increasing the oxidation rate of the particles (illustrated in Figure~\ref{fgr:full_oscillation}). Gradually, as the particles toward the outlet oxidizes the turn-over will increase and the general CO concentration will decrease promoting more and more particles to oxidize which will gradually be seen in the QMS as an increase in CO$_2$ and a decrease in CO. As the CO concentration decreases the light-off temperature will decrease hence approaching the constant temperature of the sample resulting in a steep increase in reactivity. It is important to note that the fraction of oxidized particles needed to achieve full conversion is not known. We are currently investigating new methods for gaining insight into the nature of the nanoparticles in the reactor but the low coverage and the design of the reactor !!! and the fact that the lid can only be removed by mechanically breaking the reactor!!! makes this a challenging task. If not all particles are oxidized at light-off they will now oxidize much faster due to the low CO-concentration. The further increased rate will not be visible in the QMS since the reactor is already in full conversion. As most of the particles are now oxidized they will become more and more roughened and gradually return to the reduced state. Fewer and fewer oxidized particles will be responsible for the activity increasing the roughing rate of the remaining active particles. Just before the overall activity drops only a fraction of the particles participates in the reaction and the deactivation will happen very suddenly. Once these potentially few particles eventually becomes sufficiently rough they will reduce and lose activity hence completing the oscillation cycle. It should be noted that our group has recently measured turnover frequencies of CO oxidation on Pt of almost $10^{5}$s$^{-1}$ per site corresponding to as little as $\sim$50000 Pt nanoparticles contributing to the reactivity just before the end of the high-activity cycle. This corresponds to an area of $\sim$0.5 ppm of the reactor area suggesting that in situ studies become challenging as such a minority of the reactor volume could account for all the reactivity. Attempts to see any thermal signal from such small areas has so far been in vain, !!! which would point towards a constant temperature even on the microscopic scale, however the experimental data are so far not good enough to make final conclusions.!!!

### 2012-11-24 supplementary.tex
First version of reply to referees sent to Ib

>>>>

\section{TEM Imaging}
!!! It is quite obvious that it would be very interesting to aquire good TEM images of the nanoparticles  before and after a long oscillation measurement. However, due to the design of the $\mu$-reactor platform it is extremely difficult to get TEM images after reaction. This is partly due to the very thick substrate of seveal hundred $\mu$m, as well as the anodic bonding. The lid can only be removed by mechanically breaking the device. Figure ???? show a TEM image of a cluster ...... !!!
